Iterative Monomorphisation

### 2024-03-20 iterative_monomorphisation.tex
hopefully made a couple things clearer

\SetKwData{MonoCap}{mono\_cap}\SetKwData{MonoMult}{mono\_mult}\SetKwData{MonoFloor}{mono\_floor}
\SetKwData{PolyCap}{poly\_cap}\SetKwData{PolyMult}{poly\_mult}\SetKwData{PolyFloor}{poly\_floor}
\SetKwData{TypeVars}{type\_variables}
\SetKwData{MaxMono}{max\_mono\_args}
\SetKwData{MaxPoly}{max\_poly\_args}
\SetKwData{UsedSubst}{\(S\)}

@@

The set of substitutions generated in this way is then iterated over.
Each substitution is applied to all polymorphic type argument tuples such that at least one type variable in the tuple is instantiated by the substitution. %This condition filters out all substitution application that would have otherwise left all type arguments unchanged.

@@

Depending on the shape and size of the input problem and the number of iterations performed, the doubly exponential growth may be problematic. Introducing bounds addresses this potential issue. The limit on the number of new monomorphic type arguments (in \textcolor{ourblueviolet}{blue}) has three components:
\begin{enumerate}
   \item \textcolor{ourblueviolet}{\MonoCap} is an absolute limit on the total number of new type argument tuples.
   \item \textcolor{ourblueviolet}{\MonoMult} is used to allow the total number of type argument tuples to increase by a certain proportion of the current number of type argument tuples.
   \item \textcolor{ourblueviolet}{\MonoFloor} balances out \textcolor{ourblueviolet}{\MonoMult}. It prevents \textcolor{ourblueviolet}{\MonoMult} from inhibiting new type argument tuple generation if the total number of type argument tuples is low.
\end{enumerate}

>>>>

\SetKwData{MonoCap}{\textcolor{ourblueviolet}{mono\_cap}}
\SetKwData{MonoMult}{\textcolor{ourblueviolet}{mono\_mult}}
\SetKwData{MonoFloor}{\textcolor{ourblueviolet}{mono\_floor}}
\SetKwData{PolyCap}{poly\_cap}\SetKwData{PolyMult}{poly\_mult}\SetKwData{PolyFloor}{poly\_floor}
\SetKwData{TypeVars}{type\_variables}
\SetKwData{MaxMono}{max\_mono\_args}
\SetKwData{MaxPoly}{max\_poly\_args}
\SetKwData{UsedSubst}{\(S\)}

@@

The set of substitutions generated in this way is then iterated over.
Each substitution is applied to all polymorphic type argument tuples such that at least one type variable in the tuple is instantiated by the substitution.

@@

   Depending on the shape and size of the input problem and the number of iterations performed, the doubly exponential growth may be problematic. Introducing bounds addresses this potential issue. The limit on the number of new monomorphic type argument tuples is \(\emph{min}(\emph{max}(\MonoMult\cdot n, \MonoFloor), \MonoCap)\), where \(n\) is the total number of monomorphic type argument tuples. The components of this limit are:
\begin{enumerate}
   \item \MonoCap, an absolute limit on the total number of new type argument tuples.
   \item \MonoMult, it is used to allow the total number of (monomorphic) type argument tuples to grow by a certain proportion of the current number \(n\) of monomorphic type argument tuples.
   \item \MonoFloor, which balances out \MonoMult. It prevents \MonoMult from inhibiting new type argument tuple generation if \(n\) is too low.
\end{enumerate}
